---
title: "Branch Opening Results"
format:
 html:
   page-layout: full
   code-overflow: scroll
   code-fold: true
   number-sections: true
   self-contained: true
editor: source
execute: 
 warning: false
 echo: true
---

# Setup

```{r}
#| label: setup
#| message: false
#| warning: false

rm(list = ls())
gc(verbose = FALSE)

library(data.table)
library(dplyr)
library(fixest)
library(ggplot2)
# library(kableExtra)
library(DescTools)
library(stringr)
library(scales)

# Load summary statistics function
source('https://raw.githubusercontent.com/dratnadiwakara/r-utilities/refs/heads/main/summary_stat_tables.R')

data_dir <- "../data"
```



```{r}
#| label: load-opening-sample
#| message: false
#| warning: false

# Load opening analysis sample with deposit betas already calculated
# Data created by code/sample-construction/create_opening_analysis_sample_v2.0.R
opening_sample <- readRDS(file.path(data_dir, "branch_opening_analysis_sample_with_deposit_beta_v3.rds"))
setDT(opening_sample)

# Define large_bank (CPI-adjusted $100B asset cutoff) using same logic as sample-construction script
# Data: CPI from FRED (CPIAUCSL); see commented code in key_closure_results for construction
cpi <- readRDS(file.path(data_dir, "cpi.rds"))
cpi[, adj_ratio := CPI / CPI[year == 2024]]
cpi[, asset_cutoff := adj_ratio * 100000000]

all_banks <- unique(opening_sample[,.(RSSDID,yr,bank_assets)])
all_banks <- merge(all_banks, cpi[, .(year, asset_cutoff)], by.x = "yr",by.y = "year", all.x = TRUE)
large_banks <- unique(all_banks[bank_assets > asset_cutoff]$RSSDID)

rm(all_banks)
gc(verbose = FALSE)
opening_sample[, large_bank := fifelse(RSSDID %in% large_banks, 1L, 0L)]
rm(cpi)
gc(verbose = FALSE)

# Create state-year fixed effect variable
opening_sample[, state := substr(COUNTY, 1, 2)]
opening_sample[, state_yr := paste(state, yr, sep = "_")]

opening_sample <- opening_sample[!is.na(deposit_beta)]

# # Randomly keep 75% of small banks (all large banks kept) to reduce memory
# set.seed(20250127)
# small_bank_ids <- unique(opening_sample[large_bank == 0L]$RSSDID)
# small_bank_ids_keep <- sample(small_bank_ids, size = ceiling(0.75 * length(small_bank_ids)))
# opening_sample <- opening_sample[large_bank == 1L | RSSDID %in% small_bank_ids_keep]
# rm(small_bank_ids, small_bank_ids_keep)
# gc(verbose = FALSE)

cat("Opening sample loaded successfully!\n")
cat("Observations:", format(nrow(opening_sample), big.mark = ","), "\n")
cat("Years:", min(opening_sample$yr), "-", max(opening_sample$yr), "\n")
cat("Actual openings:", format(sum(opening_sample$new_branch_zip), big.mark = ","), "\n")
cat("Opening rate:", sprintf("%.4f%%", 100 * mean(opening_sample$new_branch_zip)), "\n")
cat("Mean deposit beta:", sprintf("%.4f", mean(opening_sample$deposit_beta, na.rm = TRUE)), "\n")
```
# Baseline Opening Model


```{r}
#| label: define-opening-controls
#| message: false
#| warning: false

# State-level controls with extensive covariates
setFixest_fml(
  ..ctrl_state_opening = ~ log_zip_deposits + lag_county_deposit_gr + 
                          lag_hmda_mtg_amt_gr + lag_cra_loan_amount_amt_lt_1m_gr + 
                          lag_establishment_gr + lag_payroll_gr + lmi +
                          log1p(lag_county_cra_volume)+log1p(lag_county_mortgage_volume) + log1p(family_income)| 
                          state_yr + bank_yr,
  
  # County-level controls (more parsimonious with county-year FE)
  ..ctrl_county_opening = ~ log_zip_deposits  + log1p(family_income) | county_yr + bank_yr
)

# Create coefficient labels dictionary
covariate_labels_dict <- c(
  "deposit_beta" = "Deposit Beta",
  "log_zip_deposits" = "log(Zip Deposits)",
  "lag_county_deposit_gr" = "County Deposit Growth",
  "lag_hmda_mtg_amt_gr" = "Mortgage Growth",
  "lag_cra_loan_amount_amt_lt_1m_gr" = "CRA Loan Growth",
  "log(lag_county_mortgage_vol)" = "log(County Mortgage Volume)",
  "log(lag_county_cra_vol)" = "log(County CRA Volume)",
  "lag_establishment_gr" = "Establishment Growth",
  "lag_payroll_gr" = "Payroll Growth",
  "lmi" = "Low-to-Moderate Income",
  "log1p(lag_county_cra_volume)" = "log(Lag County CRA Volume)",
  "log1p(lag_county_mortgage_volume)" = "log(Lag County Mortgage Volume)",
  # Reduced form
  "college_frac" = "College frac",
  "log(family_income)" = "log(Income)",
  "log1p(family_income)" = "log(Income)",
  "dividend_frac" = "Stock market frac",
  "factor_age_bin2" = "Age Q1-Q2",
  "factor_age_bin3" = "Age Q2-Q3",
  "factor_age_bin4" = "Age >Q3",
  "lag_county_deposit_hhi" = "County deposit HHI",
  "population_density" = "Population density",
  "sophisticated" = "Sophisticated zipcode",
  # Usage (for pandemic-era regressions)
  "change_visits" = "Drop in visits",
  "log(distance_km)" = "Log(Distance km)"
)
omit_controls <- as.vector(covariate_labels_dict)
omit_controls <- sub("^log\\(", "", omit_controls)
omit_controls <- sub("\\)$", "", omit_controls)


# Year ranges by economic regime (same as closure analysis)
yr_range <- list(2001:2007, 2008:2011, 2012:2019, 2020:2025)
```



```{r}
#| label: tbl-baseline-opening
#| message: false
#| warning: false

gc(verbose = FALSE)

# Run 6 regressions: all banks, large banks, small banks x state/county controls (one at a time to free memory)
reg_open_baseline <- list()
reg_open_baseline[[1]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = opening_sample, vcov = ~RSSDID)
gc(verbose = FALSE)
reg_open_baseline[[2]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = opening_sample, vcov = ~RSSDID)
gc(verbose = FALSE)
large_df <- opening_sample[large_bank == 1]
reg_open_baseline[[3]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = large_df, vcov = ~RSSDID)
gc(verbose = FALSE)
reg_open_baseline[[4]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = large_df, vcov = ~RSSDID)
rm(large_df)
small_df <- opening_sample[large_bank == 0]
gc(verbose = FALSE)

reg_open_baseline[[5]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = small_df, vcov = ~RSSDID)
gc(verbose = FALSE)
reg_open_baseline[[6]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = small_df, vcov = ~RSSDID)
rm(small_df)
gc(verbose = FALSE)


# Display text table
etable(reg_open_baseline,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  headers = list("All Banks" = 2, "Large Banks" = 2, "Small Banks" = 2),
  dict = covariate_labels_dict,
  order = c("Deposit Beta","log(Zip Deposits)","log(Income)","log(Lag County CRA Volume)","log(Lag County Mortgage Volume)"),
  depvar = FALSE
)
rm(reg_open_baseline)
gc(verbose = FALSE)

# LaTeX version with AER style (uncomment to use)
# etable(reg_open_baseline,
#   se.below = TRUE,
#   signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#   headers = list("All Banks" = 2, "Large Banks" = 2, "Small Banks" = 2),
#   dict = covariate_labels_dict,
#   depvar = FALSE,
#   tex = TRUE,
#   style.tex = style.tex("aer")
# )
```

```{r}
#| message: false
#| warning: false
cat("Mean opening rate by regime:\n")
cat("Full sample:", sprintf("%.6f", mean(opening_sample$new_branch_zip, na.rm = TRUE)), "\n")
cat("Large banks:", sprintf("%.6f", mean(opening_sample[large_bank == 1]$new_branch_zip, na.rm = TRUE)), "\n")
cat("Small banks:", sprintf("%.6f", mean(opening_sample[large_bank == 0]$new_branch_zip, na.rm = TRUE)), "\n")
```


# Openings by Regime



```{r}
#| label: tbl-opening-large-by-cycle
#| message: false
#| warning: false

# Persistent subsets so fixest can find data when computing vcov
large_r1 <- opening_sample[large_bank == 1 & yr %in% yr_range[[1]]]
large_r2 <- opening_sample[large_bank == 1 & yr %in% yr_range[[2]]]
large_r3 <- opening_sample[large_bank == 1 & yr %in% yr_range[[3]]]
large_r4 <- opening_sample[large_bank == 1 & yr %in% yr_range[[4]]]

opening_large_by_cycle <- list()
opening_large_by_cycle[[1]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = large_r1, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[2]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = large_r1, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[3]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = large_r2, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[4]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = large_r2, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[5]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = large_r3, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[6]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = large_r3, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[7]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = large_r4, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_large_by_cycle[[8]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = large_r4, vcov = ~RSSDID)
gc(verbose = FALSE)
rm(large_r1, large_r2, large_r3, large_r4)
gc(verbose = FALSE)
```


```{r}
#| label: tbl-opening-large-by-cycle
#| tbl-cap: "Opening Model by Regime — Large Banks"
#| message: false
#| warning: false

etable(opening_large_by_cycle,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  dict = covariate_labels_dict,
  depvar = FALSE,
  order = c("Deposit Beta")
)
rm(opening_large_by_cycle)
gc(verbose = FALSE)

# LaTeX (uncomment to use):
# etable(opening_large_by_cycle, se.below = TRUE,
#        signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#        dict = covariate_labels_dict, depvar = FALSE,
#        tex = TRUE, style.tex = style.tex("aer"), order = c("Deposit Beta"))
```

```{r}
#| label: tbl-opening-small-by-cycle
#| message: false
#| warning: false

# Persistent subsets so fixest can find data when computing vcov
small_r1 <- opening_sample[large_bank == 0 & yr %in% yr_range[[1]]]
gc(verbose = FALSE)
opening_small_by_cycle <- list()
opening_small_by_cycle[[1]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = small_r1, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_small_by_cycle[[2]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = small_r1, vcov = ~RSSDID)
gc(verbose = FALSE)
rm(small_r1)
small_r2 <- opening_sample[large_bank == 0 & yr %in% yr_range[[2]]]
opening_small_by_cycle[[3]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = small_r2, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_small_by_cycle[[4]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = small_r2, vcov = ~RSSDID)
rm(small_r2)
small_r3 <- opening_sample[large_bank == 0 & yr %in% yr_range[[3]]]
gc(verbose = FALSE)
opening_small_by_cycle[[5]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = small_r3, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_small_by_cycle[[6]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = small_r3, vcov = ~RSSDID)
rm(small_r3)
small_r4 <- opening_sample[large_bank == 0 & yr %in% yr_range[[4]]]
gc(verbose = FALSE)
opening_small_by_cycle[[7]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = small_r4, vcov = ~RSSDID)
gc(verbose = FALSE)
opening_small_by_cycle[[8]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = small_r4, vcov = ~RSSDID)
gc(verbose = FALSE)
rm(small_r4)
gc(verbose = FALSE)


etable(opening_small_by_cycle,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  dict = covariate_labels_dict,
  depvar = FALSE,
  order = c("Deposit Beta","log(Zip Deposits)","log(Income)","log(Lag County CRA Volume)","log(Lag County Mortgage Volume)")
)
rm(opening_small_by_cycle)
gc(verbose = FALSE)

# LaTeX (uncomment to use):
# etable(opening_small_by_cycle, se.below = TRUE,
#        signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#        dict = covariate_labels_dict, depvar = FALSE,
#        tex = TRUE, style.tex = style.tex("aer"), order = c("Deposit Beta"))
```


Mean opening rates by regime (large banks, then small banks):

```{r}
#| message: false
#| warning: false
cat("Large banks mean opening rate by regime:\n")
cat("2001-2007:", sprintf("%.6f", mean(opening_sample[large_bank == 1 & yr %in% yr_range[[1]]]$new_branch_zip, na.rm = TRUE)), "\n")
cat("2008-2011:", sprintf("%.6f", mean(opening_sample[large_bank == 1 & yr %in% yr_range[[2]]]$new_branch_zip, na.rm = TRUE)), "\n")
cat("2012-2019:", sprintf("%.6f", mean(opening_sample[large_bank == 1 & yr %in% yr_range[[3]]]$new_branch_zip, na.rm = TRUE)), "\n")
cat("2020-2023:", sprintf("%.6f", mean(opening_sample[large_bank == 1 & yr %in% yr_range[[4]]]$new_branch_zip, na.rm = TRUE)), "\n\n")
cat("Small banks mean opening rate by regime:\n")
cat("2001-2007:", sprintf("%.6f", mean(opening_sample[large_bank == 0 & yr %in% yr_range[[1]]]$new_branch_zip, na.rm = TRUE)), "\n")
cat("2008-2011:", sprintf("%.6f", mean(opening_sample[large_bank == 0 & yr %in% yr_range[[2]]]$new_branch_zip, na.rm = TRUE)), "\n")
cat("2012-2019:", sprintf("%.6f", mean(opening_sample[large_bank == 0 & yr %in% yr_range[[3]]]$new_branch_zip, na.rm = TRUE)), "\n")
cat("2020-2023:", sprintf("%.6f", mean(opening_sample[large_bank == 0 & yr %in% yr_range[[4]]]$new_branch_zip, na.rm = TRUE)), "\n")
```

# Reduced Form Pooled Opening Model

Replace deposit beta with demographics and concentration (college frac, income, stock market frac, age bins, county deposit HHI, population density; alternative spec uses sophisticated zipcode).

```{r}
#| label: tbl-open-rf-full
#| message: false
#| warning: false

open_rf_full <- list()
open_rf_full[[1]] <- feols(new_branch_zip ~ college_frac + dividend_frac + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_state_opening, data = opening_sample, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_full[[2]] <- feols(new_branch_zip ~ college_frac + dividend_frac + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_county_opening, data = opening_sample, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_full[[3]] <- feols(new_branch_zip ~ sophisticated  + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_state_opening, data = opening_sample, vcov = ~RSSDID)
open_rf_full[[4]] <- feols(new_branch_zip ~ sophisticated  + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_county_opening, data = opening_sample, vcov = ~RSSDID)
gc(verbose = FALSE)



rf_omit <- omit_controls[!omit_controls %in% c("Sophisticated zipcode", "Age Q1-Q2", "Age Q2-Q3", "Age >Q3", "Income", "College frac", "Stock market frac", "County deposit HHI", "Population density", "Zip Deposits")]

etable(open_rf_full,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  dict = covariate_labels_dict,
  depvar = FALSE,
  order = c("College frac", "Stock market frac", "Sophisticated zipcode", "Zip Deposits")
  # group = list(Controls = rf_omit)
)
rm(open_rf_full)
gc(verbose = FALSE)

# LaTeX (uncomment to use):
# etable(open_rf_full, se.below = TRUE, signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#        dict = covariate_labels_dict, depvar = FALSE, tex = TRUE, style.tex = style.tex("aer"),
#        order = c("College frac", "Stock market frac", "Sophisticated zipcode", "Zip Deposits"),
#        group = list(Controls = rf_omit))
```

# Reduced Form Opening Model by Bank Size

```{r}
#| label:  tbl-open-rf-by-size
#| message: false
#| warning: false

rf_large <- opening_sample[large_bank == 1 & !is.na(deposit_beta)]
rf_small <- opening_sample[large_bank == 0 & !is.na(deposit_beta)]

open_rf_by_size <- list()
open_rf_by_size[[1]] <- feols(new_branch_zip ~ college_frac + log(family_income) + dividend_frac + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_state_opening, data = rf_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[2]] <- feols(new_branch_zip ~ college_frac + log(family_income) + dividend_frac + factor_age_bin + ..ctrl_county_opening, data = rf_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[3]] <- feols(new_branch_zip ~ college_frac + log(family_income) + dividend_frac + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_state_opening, data = rf_small, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[4]] <- feols(new_branch_zip ~ college_frac + log(family_income) + dividend_frac + factor_age_bin + ..ctrl_county_opening, data = rf_small, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[5]] <- feols(new_branch_zip ~ sophisticated + log(family_income) + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_state_opening, data = rf_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[6]] <- feols(new_branch_zip ~ sophisticated + log(family_income) + factor_age_bin + ..ctrl_county_opening, data = rf_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[7]] <- feols(new_branch_zip ~ sophisticated + log(family_income) + factor_age_bin + lag_county_deposit_hhi + population_density + ..ctrl_state_opening, data = rf_small, vcov = ~RSSDID)
gc(verbose = FALSE)
open_rf_by_size[[8]] <- feols(new_branch_zip ~ sophisticated + log(family_income) + factor_age_bin + ..ctrl_county_opening, data = rf_small, vcov = ~RSSDID)
gc(verbose = FALSE)
rm(rf_large, rf_small)
gc(verbose = FALSE)


etable(open_rf_by_size,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  depvar = FALSE,
  order = c("College frac", "Stock market frac", "Sophisticated zipcode", "Zip Deposits")
  # group = list(Controls = rf_omit)
)
rm(open_rf_by_size)
gc(verbose = FALSE)

# LaTeX (uncomment to use):
# etable(open_rf_by_size, se.below = TRUE, signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#        dict = covariate_labels_dict, depvar = FALSE, tex = TRUE, style.tex = style.tex("aer"),
#        order = c("College frac", "Stock market frac", "Sophisticated zipcode", "Zip Deposits"),
#        group = list(Controls = rf_omit))
```

# Usage

Examine how changes in branch usage during the pandemic relate to opening decisions (2020–2023), following the same setup as the closure-usage analysis.

## Prepare branch visit data

```{r}
#| label: prepare-opening-usage-data
#| message: false
#| warning: false

# Load branch visit data (SafeGraph)
# Preprocessed from SafeGraph/advan; creation script not in this repo
branch_visits <- readRDS(file.path(data_dir, "bank_branch_visits_count_2019_2022.rds"))
setDT(branch_visits)
branch_visits[, yr := year(DATE_RANGE_START)]
branch_visits <- branch_visits[yr %in% c(2019, 2021)]

# Load branch characteristics to get zip codes
# Data created by https://github.com/dratnadiwakara/r-utilities/blob/main/fdic-api/sod_download_all_data_to_rds.R
branch_chars <- readRDS(file.path(data_dir,"fdic_sod_1995_2025_simple.rds"))
setDT(branch_chars)
if ("YEAR" %in% names(branch_chars)) setnames(branch_chars, "YEAR", "yr")
if ("ZIPBR" %in% names(branch_chars)) setnames(branch_chars, "ZIPBR", "zip")

# Unique UNINUMBR–zip (use most recent year per branch)
branch_zip <- branch_chars[order(UNINUMBR, -yr)][, .SD[1], by = UNINUMBR][, .(UNINUMBR, zip)]

# Merge visits with zip
branch_visits <- merge(branch_visits, branch_zip, by = "UNINUMBR")

# Average distance from home in 2019 (pre-pandemic)
distance <- branch_visits[yr == 2019, .(distance_km = mean(DISTANCE_FROM_HOME, na.rm = TRUE) / 1000), by = zip]

# Aggregate to zip level for zips with 5+ branches
branch_visits <- branch_visits[, .(no_branches = .N, number_of_visits = sum(RAW_VISIT_COUNTS, na.rm = TRUE)), by = .(zip, yr)]
branch_visits <- branch_visits[no_branches > 4]

# Change in visits 2019 → 2021
branch_visits <- dcast(branch_visits, zip ~ yr, value.var = "number_of_visits")
branch_visits[, change_visits := (`2019` - `2021`) / `2019`]

# Merge distance and winsorize
branch_visits <- merge(branch_visits, distance, by = "zip")
branch_visits[, change_visits := DescTools::Winsorize(change_visits, quantile(change_visits, probs = c(0.01, 0.99), na.rm = TRUE))]
branch_visits[, distance_km := DescTools::Winsorize(distance_km, quantile(distance_km, probs = c(0.01, 0.99), na.rm = TRUE))]
branch_visits[, zip := str_pad(zip, 5, "left", "0")]

rm(branch_chars, branch_zip, distance)
gc(verbose = FALSE)
cat("Branch usage data prepared for", nrow(branch_visits), "zip codes.\n")
```

## Openings and branch usage (2020–2023)

```{r}
#| label: tbl-open-usage-full
#| message: false
#| warning: false

# Merge opening sample with usage data; restrict to pandemic-era years
openings <- merge(opening_sample, branch_visits[, c("zip", "change_visits", "distance_km")], by.x = "zipcode", by.y = "zip")
openings <- openings[yr >= 2020]

yr_1 <- 2020
yr_2 <- 2023

# Persistent subsets for vcov
openings_full <- openings[yr %in% yr_1:yr_2]
openings_large <- openings[large_bank == 1 & yr %in% yr_1:yr_2]
openings_small <- openings[large_bank == 0 & yr %in% yr_1:yr_2]

# Full sample: baseline and with usage (one at a time to free memory)
open_usage_full <- list()
open_usage_full[[1]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = openings_full, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_full[[2]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = openings_full, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_full[[3]] <- feols(new_branch_zip ~ deposit_beta + change_visits + log(distance_km) + ..ctrl_state_opening, data = openings_full, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_full[[4]] <- feols(new_branch_zip ~ deposit_beta + change_visits + log(distance_km) + ..ctrl_county_opening, data = openings_full, vcov = ~RSSDID)
gc(verbose = FALSE)

# By bank size
open_usage_by_size <- list()
open_usage_by_size[[1]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = openings_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[2]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = openings_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[3]] <- feols(new_branch_zip ~ deposit_beta + change_visits + log(distance_km) + ..ctrl_state_opening, data = openings_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[4]] <- feols(new_branch_zip ~ deposit_beta + change_visits + log(distance_km) + ..ctrl_county_opening, data = openings_large, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[5]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_state_opening, data = openings_small, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[6]] <- feols(new_branch_zip ~ deposit_beta + ..ctrl_county_opening, data = openings_small, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[7]] <- feols(new_branch_zip ~ deposit_beta + change_visits + log(distance_km) + ..ctrl_state_opening, data = openings_small, vcov = ~RSSDID)
gc(verbose = FALSE)
open_usage_by_size[[8]] <- feols(new_branch_zip ~ deposit_beta + change_visits + log(distance_km) + ..ctrl_county_opening, data = openings_small, vcov = ~RSSDID)
gc(verbose = FALSE)
rm(openings_full, openings_large, openings_small)
gc(verbose = FALSE)

# Mean opening rates
cat("Mean opening rates (2020–2023):\n")
cat("All banks:", sprintf("%.6f", mean(openings[yr %in% yr_1:yr_2]$new_branch_zip, na.rm = TRUE)), "\n")
cat("Large banks:", sprintf("%.6f", mean(openings[large_bank == 1 & yr %in% yr_1:yr_2]$new_branch_zip, na.rm = TRUE)), "\n")
cat("Small banks:", sprintf("%.6f", mean(openings[large_bank == 0 & yr %in% yr_1:yr_2]$new_branch_zip, na.rm = TRUE)), "\n")


usage_omit <- omit_controls[!omit_controls %in% c("Deposit Beta", "Drop in visits", "Log(Distance km)", "Zip Deposits")]

etable(open_usage_full,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  headers = list("Baseline" = 2, "With Usage" = 2),
  dict = covariate_labels_dict,
  depvar = FALSE,
  order = c("Deposit Beta")
  # group = list(Controls = usage_omit)
)
rm(open_usage_full)
gc(verbose = FALSE)

# LaTeX (uncomment to use):
# etable(open_usage_full, se.below = TRUE, signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#        headers = list("Baseline" = 2, "With Usage" = 2), dict = covariate_labels_dict,
#        depvar = FALSE, tex = TRUE, style.tex = style.tex("aer"),
#        order = c("Deposit Beta"), group = list(Controls = usage_omit))
```

```{r}
etable(open_usage_by_size,
  se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
  headers = list("Large Banks" = 4, "Small Banks" = 4),
  dict = covariate_labels_dict,
  depvar = FALSE,
  order = c("Deposit Beta")
  # group = list(Controls = usage_omit)
)
rm(open_usage_by_size, openings, branch_visits)
gc(verbose = FALSE)

# LaTeX (uncomment to use):
# etable(open_usage_by_size, se.below = TRUE, signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
#        headers = list("Large Banks" = 4, "Small Banks" = 4), dict = covariate_labels_dict,
#        depvar = FALSE, tex = TRUE, style.tex = style.tex("aer"),
#        order = c("Deposit Beta"), group = list(Controls = usage_omit))
```
