\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage[longnamesfirst]{natbib}
\usepackage{lscape}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{float}
\usepackage{tabls}
\usepackage{setspace}
\usepackage{verbatim}
\usepackage{url}
\usepackage[multiple]{footmisc}
\usepackage[margin=1in]{geometry}
\usepackage{color,soul}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{ragged2e}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage{dcolumn}
\usepackage{enumerate}
\usepackage{array}
\usepackage{enumitem}
\usepackage{color}
\usepackage{hyperref}
\usepackage{epstopdf}
\usepackage[title]{appendix}
\usepackage{titlesec}
\usepackage[normalem]{ulem}
\usepackage[font=bf]{caption}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{tikz} 
\usepackage{tabularx,booktabs} 
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{graphicx}
\setcounter{MaxMatrixCols}{10}
\usepackage{siunitx}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.50.0.2960}
%TCIDATA{Codepage=65001}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=BibTeX}
%TCIDATA{LastRevised=Thursday, July 23, 2020 13:46:23}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}
\usepackage[table]{xcolor}
%\definecolor{maroon}{cmyk}{0,0.87,0.68,0.32}
%\definecolor{mygray}{gray}{0.6}
\hypersetup{
colorlinks=true,
citecolor=blue,
linkcolor=red,
}
\titlelabel{\thetitle.\quad}



\newcommand{\sigtexfigure}{Standard errors are clustered at the bank level.}


\newcommand{\adddescription}[1]{
    \begin{minipage}{0.9\textwidth}
    \vspace{0.2cm}
     #1
    \end{minipage}\\
    \vspace{0.5cm}
}
\doublespacing
%\floatstyle{ruled}
\floatstyle{plaintop}
\restylefloat{table}
\restylefloat{figure}  
\newcommand{\floatintro}[1]{
\vspace*{0.1in}
{\small
#1
}
\vspace*{0.1in}
}
%\newcommand{\sym}{}
\sloppy

\begin{document}

\title{The Decline of Branch Banking\footnote{The results and views are those of the authors and do not reflect those of the Federal Reserve Bank of Richmond, or the Federal Reserve System.  We thank seminar and conference participants at Boston College, the Federal Reserve Banks of Chicago and Philadelphia, the University of Florida, the University of Delaware/Philadelphia Fed Fintech Conference, New York Fed/NYU Stern Conference on Financial Intermediation, 2025 NFA Annual Conference, and 2025 Community Banking Research Conference.  We used ChatGPT to assist us in copy editing this manuscript, and also in constructing some of the computer code used to build our dataset.}}



\author{Rajesh P. Narayanan\thanks{Louisiana State University (rnarayan@lsu.edu)} \and Dimuthu Ratnadiwakara\thanks{The Federal Reserve Bank of Richmond (dimuthu.ratnadiwakara@gmail.com)} \and            Philip E. Strahan\thanks{  Boston College \& NBER (strahan@bc.edu)}}

\date{\small{This Version: September 2025}}

\maketitle

\begin{abstract}
\begin{singlespace}
% We study U.S. bank branch openings and closings from 2001 to 2023. Both are concentrated in areas where depositors are more sensitive to interest rates, a pattern driven by financially sophisticated households with greater adoption of digital banking. The effects are strongest for large banks, with lending playing at most a minimal role. Incumbents retain branches where depositors are less rate-sensitive and thus more profitable; entrants avoid such markets because sticky customers are difficult to attract. The COVID-19 pandemic accelerated closures by increasing digital reliance. Overall, our findings underscore depositor rate sensitivity and technology adoption as the primary forces shaping modern branch restructuring.
We study recent branch openings and closures in U.S. banking. Both are concentrated in areas where depositors are more rate-sensitive and place less value on physical access, patterns driven by financially sophisticated households with greater digital adoption. The effects are strongest for large banks, with lending playing at most a minimal role. Incumbents retain branches where depositors are less sensitive and more reliant on proximity; entrants avoid such markets because sticky customers are difficult to attract. The COVID-19 pandemic accelerated closures. Overall, depositor sophistication—through rate sensitivity and reduced reliance on branches—drives modern branch restructuring.
\end{singlespace}
\end{abstract}
\hspace{1cm}\textbf{Keywords:} deposit franchise, branch closure, digital banking


\thispagestyle{empty}

\clearpage

\input{_body_Sep_2025}

\onehalfspacing
\clearpage
\bibliographystyle{chicago}
\bibliography{resources/branchclosure}

\input{_tables_figures_Sep_2025}


\clearpage
\appendix
\renewcommand\thefigure{IA.\arabic{figure}}
\renewcommand\thetable{IA.\arabic{table}}
\pagenumbering{roman}
\setcounter{page}{1}

{\Large \noindent \textbf{Internet Appendix:} The Decline of Branch Banking}\\
Rajesh P. Narayanan; Dimuthu Ratnadiwakara; Philip E. Strahan\\

\input{_internet_appendix_Sep_2025}

\end{document}

